Background Subtraction via Deep Variation Transformation

### 2018-08-20 draft.tex
re result

%第四步空间近邻随机采样。
It is generally accepted that neighboring background pixels share a similar temporal variation.
In other words, there are some clues hidden in pixels' spatial neighbors. 
In order to benefit from the spatial context, we concatenate the pixel matrix with 3 neighboring pixel matrixes, denoted as $SM_1$, $SM_2$ and $SM_3$ respectively.
They are randomly selected in 8 nearest neighbors. 
The input matrix of our network is defined as:
\begin{equation}
H = C(H^m, SM_1, SM_2, SM_3),
\end{equation}

Where $C$ represents the concatenating process on the third dimension.
And $H$ is the input matrix of our network, which size is $d\times d\times 4$.

@@

Based on above-mentioned factors, FCN is designed as the alternative network architecture in this paper. 
The structure of our FCN for background modeling is shown in \reffig{flow_chart}. 
The proposed FCN contains 5 convolutional layers, 2 pool layers and a convolutional layer which have a filter size of $1*1$. 
We use the Rectified Linear Unit (ReLU) as activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. 
We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.

@@

% \begin{table}[tab1]
\begin{table*}[!t]				% TABLE
\centering
\caption{The performance comparison of the proposed approach and some state-of-the-art algorithms on the video sequences from different categories in CDnet 2014.}
\label{tab1}
\begin{tabular}{lllllllllllll}
\hline
Videos      & baseline & dyna.bg & cam.jitter & int.obj.m & shadow & thermal & bad.weat & low f.rate & night vid. & PTZ    & turbul. & overall \\ \hline
DeepBS\cite{Babaee2017deep}      & 0.9580   & 0.8761  & \textbf{0.8990}     & 0.6097    & \textbf{0.9304} & 0.7583  & 0.8647   & 0.5900     & 0.6359     & 0.3306 & 0.8993  & 0.7458  \\
IUTIS-5\cite{Bianco2017TEC}     & 0.9567   & 0.8902  & 0.8332     & 0.7296    & 0.9084 & 0.8303  & 0.8289   & \textbf{0.7911}     & 0.5132     & 0.4703 & 0.8507  & 0.7717  \\
FTSG\cite{Wang2014FTSG}        & 0.9330   & 0.8792  & 0.7513     & 0.7891    & 0.8832 & 0.7768  & 0.8228   & 0.6259     & 0.5130     & 0.3241 & 0.7127  & 0.7283  \\
AAPSA\cite{RAMIREZALONSO2016990}       & 0.9183   & 0.6706  & 0.7207     & 0.5098    & 0.7953 & 0.7030  & 0.7742   & 0.4942     & 0.4161     & 0.3302 & 0.4643  & 0.6179  \\
CwisarDH\cite{Gregorio2014CwisarDH}    & 0.9145   & 0.8274  & 0.7886     & 0.5753    & 0.8581 & 0.7866  & 0.6837   & 0.6406     & 0.3735     & 0.3218 & 0.7227  & 0.6812  \\
PAWCS\cite{Charles2015PAWCS}       & 0.9397   & 0.8938  & 0.8137     & 0.7764    & 0.8934 & 0.8324  & 0.8059   & 0.6433     & 0.4171     & 0.4450 & 0.7667  & 0.7403  \\
SuBSENSE\cite{St-Charles2015SuBSENSE}    & 0.9503   & 0.8177  & 0.8152     & 0.6569    & 0.8986 & 0.8171  & 0.8594   & 0.6594     & 0.4918     & 0.3894 & 0.8423  & 0.7408  \\
SemanticBGS\cite{Braham2017Semantic} & 0.9604   & \textbf{0.9489}  & 0.8388     & 0.7878    & 0.9244 & 0.8219  & 0.8260   & 0.7888     & 0.5014     & 0.5673 & 0.6921  & 0.7892  \\
MBS\cite{Multimode_Background_Subtraction}         & 0.9287   & 0.7915  & 0.8367     & 0.7568    & 0.8262 & 0.8194  & 0.7980   & 0.6350     & 0.5158     & 0.5520 & 0.5858  & 0.7288  \\
WeSamBE\cite{2017_TCSVT_BG_7938679}     & 0.9413   & 0.7440  & 0.7976     & 0.7392    & 0.8999 & 0.7962  & 0.8608   & 0.6602     & 0.5929     & 0.3844 & 0.7737  & 0.7446  \\
ShareM\cite{2015_ICME_ShareModel}      & 0.9522   & 0.8222  & 0.8141     & 0.6727    & 0.8898 & 0.8319  & 0.8480   & 0.7286     & 0.5419     & 0.3860 & 0.7339  & 0.7474  \\
GMM\cite{Zivkovic2004}         & 0.8245   & 0.633   & 0.5969     & 0.5207    & 0.7370 & 0.6621  & 0.7380   & 0.5373     & 0.4097     & 0.1522 & 0.4663  & 0.5707  \\
RMoG\cite{Varadarajan2013}        & 0.7848   & 0.7352  & 0.7010     & 0.5431    & 0.7212 & 0.4788  & 0.6826   & 0.5312     & 0.4265     & 0.2470 & 0.4578  & 0.5735  \\ \hline
DPVTL        & \textbf{0.9757}   & 0.9303  & 0.8850     & \textbf{0.9322}    & 0.9274 & \textbf{0.9348}  & \textbf{0.8659}   & 0.7489     & \textbf{0.7529}     & \textbf{0.5836} & \textbf{0.9005}  & \textbf{0.8636} \\ \hline
\end{tabular}
\end{table*}

\begin{table*}[!t]
\centering
\caption{The performance comparison of the proposed approach and some classical methods and deep-based method DBMF .}
\label{tab2}
\begin{tabular}{llllllll}
\hline
Methods  & highway & office & Pedestrians & PETS2006 & Fall   & sofa   & overall \\ \hline
GMM\cite{Stauffer1999}      & 0.5788  & 0.2338 & 0.5202      & 0.6011   & 0.8026 & 0.5225 & 0.5432  \\
CodeBook\cite{WU2010739} & 0.8356  & 0.5939 & 0.7293      & 0.7808   & 0.3921 & 0.8149 & 0.6911  \\
ViBe\cite{Barnich2011_2011_TIP}     & 0.7535  & 0.6676 & 0.8367      & 0.6668   & 0.6829 & 0.4298 & 0.6729  \\
PBAS\cite{Hofmann2012Background}     & 0.8071  & 0.6839 & 0.7902      & 0.7280   & 0.3420 & 0.5768 & 0.6547  \\
P2M\cite{Yang2016P2M}      & 0.9160  & 0.3849 & 0.9121      & 0.7322   & 0.5819 & 0.4352 & 0.6604  \\
DBMF\cite{Yang2018DBMF}     & 0.9412  & 0.9236 & 0.8394      & 0.9059   & 0.8203 & 0.8645 & 0.8824  \\ \hline
DPVTL     & \textbf{0.9827}  & \textbf{0.9719} & \textbf{0.9729}      & \textbf{0.9753}   & \textbf{0.9269} & \textbf{0.9103} & \textbf{0.9567}  \\ \hline
\end{tabular}
\end{table*}

    \begin{table*}[!t]
\centering
\caption{The performance comparison of the proposed approach and some state-of-the-art algorithms on the video sequences from different categories in CAMO-UOW.}
\label{tab3}
\begin{tabular}{lllllllllll}
\hline
Methods  & MOG2\cite{ZIVKOVIC2006773} & FCI\cite{Baf2008FCI}  & LBA-SOM\cite{LBA-SOM2008} & PBAS & SuBSENSE & ML-BGS\cite{ML-BGS2007} & DECOLOR\cite{DECOLOR2013}       & COROLA\cite{SHAKERI201628} & FWFC\cite{Li2018CAMO}          & Ours          \\ \hline
Video 1  & 0.79 & 0.88 & 0.8     & 0.9  & 0.89     & 0.89   & 0.92          & 0.8    & \textbf{0.94} & \textbf{0.94} \\
Video 2  & 0.82 & 0.79 & 0.8     & 0.82 & 0.88     & 0.8    & 0.83          & 0.58   & 0.96          & \textbf{0.98} \\
Video 3  & 0.88 & 0.86 & 0.85    & 0.91 & 0.9      & 0.8    & 0.9           & 0.82   & \textbf{0.94} & \textbf{0.94} \\
Video 4  & 0.89 & 0.9  & 0.76    & 0.93 & 0.78     & 0.88   & 0.95          & 0.87   & 0.94          & \textbf{0.97} \\
Video 5  & 0.84 & 0.86 & 0.82    & 0.83 & 0.82     & 0.8    & 0.82          & 0.75   & 0.91          & \textbf{0.97} \\
Video 6  & 0.93 & 0.87 & 0.77    & 0.95 & 0.92     & 0.95   & \textbf{0.97} & 0.72   & 0.94          & 0.96          \\
Video 7  & 0.76 & 0.83 & 0.88    & 0.91 & 0.87     & 0.79   & 0.91          & 0.83   & 0.96          & \textbf{0.99} \\
Video 8  & 0.83 & 0.87 & 0.85    & 0.87 & 0.93     & 0.86   & 0.86          & 0.68   & 0.96          & \textbf{0.98} \\
Video 9  & 0.89 & 0.9  & 0.87    & 0.84 & 0.92     & 0.87   & 0.86          & 0.78   & 0.88          & \textbf{0.99} \\
Video 10 & 0.89 & 0.86 & 0.89    & 0.91 & 0.92     & 0.9    & 0.94          & 0.85   & 0.96          & \textbf{0.97} \\ \hline
average  & 0.85 & 0.86 & 0.83    & 0.89 & 0.88     & 0.85   & 0.90          & 0.77   & 0.94          & \textbf{0.97} \\ \hline
\end{tabular}
\end{table*}

@@

All these experiments of the proposed method were implemented in matlab and ran on the computer with Nvidia tasela K80 GPU and all images are keep their original resolution. 
For each video in CDnet 2014, 100 training frames are extracted to produce the image matrix. 
It should be noted that the 100 frames only accounts for less than 10\% of total Groundtruth in CDnet 2014. 
In contrast, 90\% of data were used as training samples in the DBMF, which suggest that the proposed approach achieves well performance with limited training frames. 
Considering that the videos in CAMO-UOW have fewer frames, we reduce the number of training frames to 49. 
During the experience, the training set and testing set are completely separated. 
More specifically, our FCN network is random initialized. 
We train the network with mini-batches of size 100, a learning rate $α = 1 ∗ 10^{−3}$ over 20 epochs. 
The last threshold $R$ is set to 0.6.

>>>>

%第四步空间近邻随机采样。
It is generally accepted that neighboring background pixels share a similar temporal variation.
In other words, there are some clues hidden in pixels' spatial neighbors. 
In order to benefit from the spatial context, we concatenate the pixel matrix with 2 neighboring pixel matrixes, denoted as $SM_1$, $SM_2$ and $SM_3$ respectively.
They are randomly selected in 8 nearest neighbors. 
The input matrix of our network is defined as:
\begin{equation}
H = C(H^m, SM_1, SM_2),
\end{equation}

Where $C$ represents the concatenating process on the third dimension.
And $H$ is the input matrix of our network, which size is $d\times d\times 3$.

@@

Based on above-mentioned factors, FCN is designed as the alternative network architecture in this paper. 
The structure of our FCN for background modeling is shown in \reffig{flow_chart}. 
The proposed FCN contains 5 convolutional layers and a convolutional layer which have a filter size of $1*1$. 
We use the Rectified Linear Unit (ReLU) as activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. 
We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.

@@

% \begin{table}[tab1]
\begin{table*}[!t]				% TABLE
\centering
\caption{The performance comparison of the proposed approach and some state-of-the-art algorithms on the video sequences from different categories in CDnet 2014.}
\label{tab1}
\begin{tabular}{lllllllllllll}
\hline
Videos      & baseline & dyna.bg & cam.jitter & int.obj.m & shadow & thermal & bad.weat & low f.rate & night vid. & PTZ    & turbul. & overall \\ \hline
DeepBS\cite{Babaee2017deep}      & 0.9580   & 0.8761  & 0.8990     & 0.6097    & 0.9304 & 0.7583  & 0.8647   & 0.5900     & 0.6359     & 0.3306 & 0.8993  & 0.7458  \\
IUTIS-5\cite{Bianco2017TEC}     & 0.9567   & 0.8902  & 0.8332     & 0.7296    & 0.9084 & 0.8303  & 0.8289   & \textbf{0.7911}     & 0.5132     & 0.4703 & 0.8507  & 0.7717  \\
FTSG\cite{Wang2014FTSG}        & 0.9330   & 0.8792  & 0.7513     & 0.7891    & 0.8832 & 0.7768  & 0.8228   & 0.6259     & 0.5130     & 0.3241 & 0.7127  & 0.7283  \\
AAPSA\cite{RAMIREZALONSO2016990}       & 0.9183   & 0.6706  & 0.7207     & 0.5098    & 0.7953 & 0.7030  & 0.7742   & 0.4942     & 0.4161     & 0.3302 & 0.4643  & 0.6179  \\
CwisarDH\cite{Gregorio2014CwisarDH}    & 0.9145   & 0.8274  & 0.7886     & 0.5753    & 0.8581 & 0.7866  & 0.6837   & 0.6406     & 0.3735     & 0.3218 & 0.7227  & 0.6812  \\
PAWCS\cite{Charles2015PAWCS}       & 0.9397   & 0.8938  & 0.8137     & 0.7764    & 0.8934 & 0.8324  & 0.8059   & 0.6433     & 0.4171     & 0.4450 & 0.7667  & 0.7403  \\
SuBSENSE\cite{St-Charles2015SuBSENSE}    & 0.9503   & 0.8177  & 0.8152     & 0.6569    & 0.8986 & 0.8171  & 0.8594   & 0.6594     & 0.4918     & 0.3894 & 0.8423  & 0.7408  \\
SemanticBGS\cite{Braham2017Semantic} & 0.9604   & \textbf{0.9489}  & 0.8388     & 0.7878    & 0.9244 & 0.8219  & 0.8260   & 0.7888     & 0.5014     & 0.5673 & 0.6921  & 0.7892  \\
MBS\cite{Multimode_Background_Subtraction}         & 0.9287   & 0.7915  & 0.8367     & 0.7568    & 0.8262 & 0.8194  & 0.7980   & 0.6350     & 0.5158     & 0.5520 & 0.5858  & 0.7288  \\
WeSamBE\cite{2017_TCSVT_BG_7938679}     & 0.9413   & 0.7440  & 0.7976     & 0.7392    & 0.8999 & 0.7962  & 0.8608   & 0.6602     & 0.5929     & 0.3844 & 0.7737  & 0.7446  \\
ShareM\cite{2015_ICME_ShareModel}      & 0.9522   & 0.8222  & 0.8141     & 0.6727    & 0.8898 & 0.8319  & 0.8480   & 0.7286     & 0.5419     & 0.3860 & 0.7339  & 0.7474  \\
GMM\cite{Zivkovic2004}         & 0.8245   & 0.633   & 0.5969     & 0.5207    & 0.7370 & 0.6621  & 0.7380   & 0.5373     & 0.4097     & 0.1522 & 0.4663  & 0.5707  \\
RMoG\cite{Varadarajan2013}        & 0.7848   & 0.7352  & 0.7010     & 0.5431    & 0.7212 & 0.4788  & 0.6826   & 0.5312     & 0.4265     & 0.2470 & 0.4578  & 0.5735  \\ \hline
DPVTL        & \textbf{0.9811}   & 0.9329  & \textbf{0.9014}     & \textbf{0.9595}    & \textbf{0.9467} & \textbf{0.9479}  & \textbf{0.8780}   & 0.7818     & \textbf{0.7737}     & \textbf{0.5957} & \textbf{0.9034}  & \textbf{0.8789} \\ \hline
\end{tabular}
\end{table*}

\begin{table*}[!t]
\centering
\caption{The performance comparison of the proposed approach and some classical methods and deep-based method DBMF .}
\label{tab2}
\begin{tabular}{llllllll}
\hline
Methods  & highway & office & Pedestrians & PETS2006 & Fall   & sofa   & overall \\ \hline
GMM\cite{Stauffer1999}      & 0.5788  & 0.2338 & 0.5202      & 0.6011   & 0.8026 & 0.5225 & 0.5432  \\
CodeBook\cite{WU2010739} & 0.8356  & 0.5939 & 0.7293      & 0.7808   & 0.3921 & 0.8149 & 0.6911  \\
ViBe\cite{Barnich2011_2011_TIP}     & 0.7535  & 0.6676 & 0.8367      & 0.6668   & 0.6829 & 0.4298 & 0.6729  \\
PBAS\cite{Hofmann2012Background}     & 0.8071  & 0.6839 & 0.7902      & 0.7280   & 0.3420 & 0.5768 & 0.6547  \\
P2M\cite{Yang2016P2M}      & 0.9160  & 0.3849 & 0.9121      & 0.7322   & 0.5819 & 0.4352 & 0.6604  \\
DBMF\cite{Yang2018DBMF}     & 0.9412  & 0.9236 & 0.8394      & 0.9059   & 0.8203 & 0.8645 & 0.8824  \\ \hline
DPVTL     & \textbf{0.9888}  & \textbf{0.9819} & \textbf{0.9728}      & \textbf{0.9808}   & \textbf{0.9394} & \textbf{0.9333} & \textbf{0.9662}  \\ \hline
\end{tabular}
\end{table*}

    \begin{table*}[!t]
\centering
\caption{The performance comparison of the proposed approach and some state-of-the-art algorithms on the video sequences from different categories in CAMO-UOW.}
\label{tab3}
\begin{tabular}{lllllllllll}
\hline
Methods  & MOG2\cite{ZIVKOVIC2006773} & FCI\cite{Baf2008FCI}  & LBA-SOM\cite{LBA-SOM2008} & PBAS & SuBSENSE & ML-BGS\cite{ML-BGS2007} & DECOLOR\cite{DECOLOR2013}       & COROLA\cite{SHAKERI201628} & FWFC\cite{Li2018CAMO}          & Ours          \\ \hline
Video 1  & 0.79 & 0.88 & 0.8     & 0.9  & 0.89     & 0.89   & 0.92          & 0.8    & 0.94 & \textbf{0.96} \\
Video 2  & 0.82 & 0.79 & 0.8     & 0.82 & 0.88     & 0.8    & 0.83          & 0.58   & 0.96          & \textbf{0.98} \\
Video 3  & 0.88 & 0.86 & 0.85    & 0.91 & 0.9      & 0.8    & 0.9           & 0.82   & 0.94 & \textbf{0.95} \\
Video 4  & 0.89 & 0.9  & 0.76    & 0.93 & 0.78     & 0.88   & 0.95          & 0.87   & 0.94          & \textbf{0.98} \\
Video 5  & 0.84 & 0.86 & 0.82    & 0.83 & 0.82     & 0.8    & 0.82          & 0.75   & 0.91          & \textbf{0.98} \\
Video 6  & 0.93 & 0.87 & 0.77    & 0.95 & 0.92     & 0.95   & 0.97	      & 0.72   & 0.94          & \textbf{0.98}  \\
Video 7  & 0.76 & 0.83 & 0.88    & 0.91 & 0.87     & 0.79   & 0.91          & 0.83   & 0.96          & \textbf{0.99} \\
Video 8  & 0.83 & 0.87 & 0.85    & 0.87 & 0.93     & 0.86   & 0.86          & 0.68   & \textbf{0.96}          & \textbf{0.96} \\
Video 9  & 0.89 & 0.9  & 0.87    & 0.84 & 0.92     & 0.87   & 0.86          & 0.78   & 0.88          & \textbf{0.99} \\
Video 10 & 0.89 & 0.86 & 0.89    & 0.91 & 0.92     & 0.9    & 0.94          & 0.85   & 0.96          & \textbf{0.97} \\ \hline
average  & 0.85 & 0.86 & 0.83    & 0.89 & 0.88     & 0.85   & 0.90          & 0.77   & 0.94          & \textbf{0.97} \\ \hline
\end{tabular}
\end{table*}

@@

All these experiments of the proposed method were implemented in matlab and ran on the computer with Nvidia tasela K80 GPU and all images are keep their original resolution. 
For each video in CDnet 2014, 100 training frames are extracted to produce the image matrix. 
It should be noted that the 100 frames only accounts for less than 10\% of total Groundtruth in CDnet 2014. 
In contrast, 90\% of data were used as training samples in the DBMF, which suggest that the proposed approach achieves well performance with limited training frames. 
Considering that the videos in CAMO-UOW have fewer frames, we reduce the number of training frames to 49. 
During the experience, the training set and testing set are completely separated. 
More specifically, our FCN network is random initialized. 
We train the network with mini-batches of size 200, a learning rate $α = 1 ∗ 10^{−3}$ over 20 epochs. 
The last threshold $R$ is set to 0.6.
